### 2019-04-02 Thesis/games.tex
Nightly commit (not in a compiling state rn).

\section{The Strategy $\cell$}

@@

      This tells us that we can assume that $\Gamma$ is the empty context when we want to deal with these two cases.

@@

              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt, dotted]}, bend left=5] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]

@@

      Now we have a commutative diagram

@@

@@

>>>>

\section{The Strategy $\cell$}
\label{SecCell}

@@

      This tells us that we can assume that $\Gamma$ is the empty context, so that the rules take on the form
        x,s\ts x\gets n \oopto x,(x\mapsto n)\ts \skipp
        x,s \ts \oc x \oopto x,s\ts s(x)\,.

@@

              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]

@@

      Now the commutative diagrams in Figure \ref{FigSoundnessOoptoStorage} deal with these last two cases.\qedhere

@@

        \caption[Diagrams to prove that the conclusion of Lemma \ref{LemSoundnessOopto} holds for the storage cell rules.]{Diagrams to prove that the conclusion of Lemma \ref{LemSoundnessOopto} holds for the storage cell rules.  
        References in the middle of a shape refer to Lemma \ref{LemCellProjections} and Proposition \ref{PropFormulaForAlpha} above.  
        Note the prominent role played in both diagrams by the anamorphism square for $\cell$ as in Section \ref{SecCell}.}
        \label{FigSoundnessOoptoStorage}

@@

Now that we have dealt with the base rules, we can move on to the full relation $\opto$.

\begin{lemma}
  The relation $\opto$ between triples $\Gamma,s\ts M$ preserves the composite
  \[
    \oc\deno s;\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,.
    \]
  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, and $\EE$ is a context of type $U$ with a hole of type $T$, then the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=24pt]
      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts \EE[M]}\tensor \oc V_\Gamma"] \\
      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
        &
          &
            & \deno U \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno U,\oc \V_{\Gamma}}}"] \\
      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
        &
          &
            &  \deno{U}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{U} \sequoid (\Gamma+0_\Delta)}"] \\
      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts \EE[N]} \tensor \oc \V_{\Gamma,\Delta}}"]
        &
          & {\deno U \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno U,\oc \V_{\Gamma,\Delta}}}"]
            & {{\deno U \sequoid \oc \V_{\Gamma,\Delta}}\,,}
    \end{tikzcd}
    \]
\end{lemma}
\begin{proof}
  We use Lemma
  \[
    \begin{tikzcd}
      I \arrow[r, "\deno s"] \arrow[d, "\deno s"']
        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "\lunit_{S_\Gamma}" description]
          & \oc \V_\Gamma \arrow[d, "\lunit_{\oc\V_\Gamma}"'] \\
      \oc S_\Gamma \arrow[d, "\cell"'] \arrow[dr, "\mu_{S_\Gamma}" description]
        & I \tensor \oc S_\Gamma \arrow[r, "I\tensor \cell" description] \arrow[d, "\deno s \tensor \oc S_\Gamma" description]
          & I \tensor \oc\V_\Gamma \arrow[d, "\deno s \tensor \oc\V_\Gamma"] \\
      \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"'] \arrow[dr, "\mu_{\V_\Gamma}" description]
        & \oc S_\Gamma \tensor \oc S_\Gamma \arrow[d, "\cell\tensor\cell" description] \arrow[r, "\oc S_\Gamma\tensor \cell" description]
          & \oc S_\Gamma \tensor \oc\V_\Gamma \arrow[dl, "\cell\tensor\oc \V_\Gamma"] \\
      \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"']
        & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"]
          & \\
      (\oc\V_\Gamma\tensor\oc\V_\Gamma) \tensor\oc\V_\Gamma \arrow[r, "{\sym^{(23)}_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}}" description] \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma"']
        & (\oc\V_\Gamma\tensor\oc\V_\Gamma) \tensor\oc\V_\Gamma \arrow[r, "(\deno{\Gamma\ts M}\tensor\sigma)\tensor\oc\V_\Gamma"] \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma" description]
          & (\deno T\tensor A)\tensor\oc\V_\Gamma \arrow[d, "{\wk_{\deno T,A}\tensor\oc\V_\Gamma}"] \\
      (\deno T \tensor \oc\V_\Gamma)\tensor\oc\V_\Gamma \arrow[r, "{\sym^{(23)}_{\deno T,\oc\V_\Gamma,\oc\V_\Gamma}}" description] \arrow[d, "{
\end{proof}
